QPLIB: A Library of Quadratic Programming Instances

### 2016-07-21 QPLIB-3.tex
comments and minor corrections from first proofreading
nimg: added QPLIB format section, currently in appendix       Updated main document to reflect this, and added nimg coordinates       Alightly updated Section 3 to reflect QPLIB format

In this Section we present all the steps performed in order to build the library. In particular we describe the first set of gathered instances (Section \ref{subsec:instColl}), we discuss the issues concerning the format of the instances (Section \ref{subsec:format}), we present the feature used to classified the instances (Section \ref{subsec:feature}), and finally we then describe the selection process that we have used to filter the instances in order to construct the final library (Section \ref{subsec:selection}).

@@

As second format, we introduced 
a specific format \texttt{.qplib}. This new format is capable to describe all the instances of the library in a sparse form. 
In comparison to a more \emph{high level} format like \texttt{.gms}, the new format presents two advantages:  
it is easier to read by a self-made parser and it produces smaller files.
\textcolor{red}{ToDo: describe \texttt{.qplib} format. Maybe in an appendix?}

>>>>

In this section we present all the steps performed in order to build the library. In particular we describe the first set of gathered instances (Section \ref{subsec:instColl}), we discuss the issues concerning the format of the instances (Section \ref{subsec:format}), we present the feature used to classified the instances (Section \ref{subsec:feature}), and finally we then describe the selection process that we have used to filter the instances in order to construct the final library (Section \ref{subsec:selection}).

@@

In addition, we have introduced
a specific format \texttt{.qplib}. This new format is capable of describing
all the instances of the library in a sparse form.
In comparison to a more \emph{high level} format like \texttt{.gms}, the new
format presents two advantages:
it is easier to read by a self-made parser and it produces smaller files.
See Appendix~\label{sec:format} for details.
%\textcolor{red}{ToDo: describe \texttt{.qplib} format. Maybe in an appendix?}
